### 2025-09-24 paper/sec/introduction.tex
rough pass over future work.

Taken together, these categories cover a representative portion of the numerical reasoning idioms found in the
SciGen benchmark. However, some linguistic forms that commonly arise in scholarly articles are not covered in
our analysis. We have yet to study approximate quantitative terms like \textfrag{around 50\%} or
\textfrag{roughly 100 instances}, nor interval-based descriptions such as \textfrag{between 30 and 40\%} or
\textfrag{within 5–10 seconds}. While we have no reason for thinking these will present specific difficulties,
other forms are likely to be more challenging. So-called \emph{graded} modal adverbs~\citep{lassiter17} which
modify adjectival comparatives like \textfrag{better} -- as in \textfrag{slightly better} and
\textfrag{significantly higher} -- especially when combined with trends over time, as in \textfrag{steadily
increasing} or \textfrag{sharply declining} -- are likely to prove difficult because the interpretation of
these qualifiers can be subjective and context-dependent. Adverbial quantifiers like \textfrag{generally} and
\textfrag{usually} present similar challenges because colloquial use may differ from more formal uses (in some
situations ``most'' might mean a majority, i.e.~greater than 50\% of cases, but in others may mean only
``greater than any other alternative proportion''). On the other hand these difficulties also present
themselves to human readers, so extending coverage to these idioms would substantially deepen our tool's
ability to bridge natural language reporting with interpretation in terms of the underlying dataset, perhaps
revealing inconsistent use of technical language on the part of the author. We discuss this further in
\secref{conclusion:future-work}.

>>>>

Taken together, these categories cover a representative portion of the numerical reasoning idioms found in the
SciGen benchmark. However, some linguistic forms that commonly arise in scholarly articles are not covered in
our analysis. We have yet to study approximate quantitative terms like \textfrag{around 50\%} or
\textfrag{roughly 100 instances}, nor interval-based descriptions such as \textfrag{between 30 and 40\%} or
\textfrag{within 5–10 seconds}. While we have no reason for thinking these will present specific difficulties,
other forms are likely to be more challenging. So-called \emph{graded} modal adverbs~\citep{lassiter17} which
modify adjectival comparatives like \textfrag{better} -- as in \textfrag{slightly better} and
\textfrag{significantly higher} -- especially when combined with trends over time, as in \textfrag{steadily
increasing} or \textfrag{sharply declining} -- are likely to prove difficult because the interpretation of
these qualifiers can be subjective and context-dependent. Generalised quantifiers like \textfrag{generally}
and \textfrag{usually}~\citep{barwise81} present similar challenges because colloquial use may differ from
more formal uses (in some situations ``most'' might mean a majority, i.e.~greater than 50\% of cases, but in
others may mean only ``greater than any other alternative proportion''). On the other hand these difficulties
also present themselves to human readers, so extending coverage to these idioms would substantially deepen our
tool's ability to bridge natural language reporting with interpretation in terms of the underlying dataset,
perhaps revealing inconsistent use of technical language on the part of the author. We discuss this further in
\secref{conclusion:future-work}.
